The illusory promise of the Aligned Rank Transform

### 2025-12-10 text/66-Results-Interactions.qmd
starting new revisions

::: {#fig-ratio-interaction-2}
```{r, echo=FALSE, message=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
distributions <- c("norm", "lnorm", "exp", "cauchy", "poisson", "binom")
dnames <- c("Normal", "Log-normal", "Exponential", "Cauchy", "Poisson", "Binomial")
alpha <- .05
prefix <- "1_test_4x3_Ratio"
df <- readlyData(prefix, alpha, 0, distributions, dnames)

#xlab <- TeX("\\text{main effect of factors }X_1\\text{ and }X_2\\text{ }(a_1 = a_2)")
plotlyError(df, xlab = "magnitude of main effects", var = "rateX1X2", xvar = "effectX1", max = 105)
```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitudes $a_1 = a_2$ of the main effects of $X_1$ and $X_2$. *Note: Type I errors are defined based on the null hypothesis $a_{12} = 0$. A different definition may lead to different results.* 
:::

@@

::: {#fig-ordinal-interaction-2}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "2_test_4x3_Ordinal"
distributions <- c("likert5", "likert5B", "likert7", "likert7B", "likert11", "likert11B")
dnames <- c("5 - equidistant", "5 - flexible", "7 - equidistant", "7 - flexible", "11 - equidistant", "11 - flexible")

df <- readlyData(prefix, alpha, 0, distributions, dnames)
plotlyError(df, xlab = "magnitude of main effects", var = "rateX1X2", xvar = "effectX1", max = 105)

```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitudes $a_1 = a_2$ of the main effects of $X_1$ and $X_2$. *Note: Type I errors are defined based on the null hypothesis $a_{12} = 0$. A different definition may lead to different results.*
:::

@@

::: {#fig-designs-interaction-2}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "3_test-Designs"
distributions <- c("norm", "lnorm", "exp", "poisson", "binom", "likert5B")
dnames <- c("Normal", "Log-normal", "Exponential", "Poisson", "Binomial", "Ordinal (5 levels)")

df <- readData(prefix, n = 20, alpha, effectType = 0, distributions)
df <- reshapeByDesign(df, dnames)
plotlyErrorByDesign(df, xlab = "magnitude of main effects", var = "rateX1X2", xvar = "effectX1", max = 105)
```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitudes $a_1 = a_2$ of the main effects of $X_1$ and $X_2$  ($n = 20$). *Note: Type I errors are defined based on the null hypothesis $a_{12} = 0$. A different definition may lead to different results.*
:::

>>>>

::: {#fig-ratio-interaction-2}
```{r, echo=FALSE, message=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
distributions <- c("norm", "lnorm", "exp", "cauchy", "poisson", "binom")
dnames <- c("Normal", "Log-normal", "Exponential", "Cauchy", "Poisson", "Binomial")
alpha <- .05
prefix <- "Type_I_4x3_ratio"
df <- readly_data(prefix, alpha, 0, distributions, dnames)

#xlab <- TeX("\\text{main effect of factors }X_1\\text{ and }X_2\\text{ }(a_1 = a_2)")
plotly_error(df, xlab = "magnitude of main effects", var = "rateX1X2", xvar = "effectX1", max = 105)
```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitudes $a_1 = a_2$ of the main effects of $X_1$ and $X_2$. *Note: Type I errors are defined based on the null hypothesis $a_{12} = 0$. A different definition may lead to different results.* 
:::

@@

::: {#fig-ordinal-interaction-2}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "Type_I_ordinal"
distributions <- c("likert_5", "likert_5_flex", "likert_7", "likert_7_flex", "likert_11", "likert_11_flex")
dnames <- c("5 - equidistant", "5 - flexible", "7 - equidistant", "7 - flexible", "11 - equidistant", "11 - flexible")

df <- readly_data(prefix, alpha, 0, distributions, dnames)
plotly_error(df, xlab = "magnitude of main effects", var = "rateX1X2", xvar = "effectX1", max = 105)
```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitudes $a_1 = a_2$ of the main effects of $X_1$ and $X_2$. *Note: Type I errors are defined based on the null hypothesis $a_{12} = 0$. A different definition may lead to different results.*
:::

@@

::: {#fig-designs-interaction-2}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "Type_I_designs"
distributions <- c("norm", "lnorm", "exp", "poisson", "binom", "likert")
dnames <- c("Normal", "Log-normal", "Exponential", "Poisson", "Binomial", "Ordinal (5 levels)")

df <- read_data(prefix, alpha, effectType = 0, distributions)
df <- reshape_by_design(df, dnames)
plotly_error_by_design(df, xlab = "magnitude of main effects", var = "rateX1X2", xvar = "effectX1", max = 105)
```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitudes $a_1 = a_2$ of the main effects of $X_1$ and $X_2$  ($n = 20$). *Note: Type I errors are defined based on the null hypothesis $a_{12} = 0$. A different definition may lead to different results.*
:::
